Resource Allocation in an Open RAN System using Network Slicing\vspace{-.1cm}

### 2021-07-01 Latex/journal_v1/V5/pr.tex
introduction extend

\begin{abstract}
Taking the advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN)
is introduced as a next generation of RAN systems which leads to increase the flexibility, Openness and 
reduce operator costs
and allow them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for different type of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different type of services in O-DU, O-CU and user plane function (UPF) is performed.
Limited fronthaul capacity and the restriction of end-to-end delay is considered in the problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB) and power allocation. The main problem is a mixed integer non-linear programming that is tremendously difficult.
To solve the challenging problem, we broke it down into two different steps that is solved by iterative algorithm.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment 
and the number of activated VNFs. In the second step, O-RU association is carried out.
The proposed method is confirmed by the simulation results in a way that
the simulations illustrate higher achievable data rate compared with a baseline scheme which only optimizes one of the baseband resources.

@@

\begin{IEEEkeywords}
Open Radio Access Network (O-RAN), Virtual Network Function (VNF), 
\end{IEEEkeywords}

\section{Introduction} 
Nowadays, RAN virtualization attracts a lot of attention from operators since it 
has significant benefits which leads to increase the flexibility and 
reduce operator costs
such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage Open Radio Access Network (O-RAN)
Alliance to establish O-RAN as a next generation of RAN systems. 
The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
CRAN, divides RAN into two parts radio remote head (RRH) and base band unit (BBU). 
More than one distributed RRHs can be connected to a centralized BBU which is named BBU-pool\cite{han2019research}.
Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
Central Unit (O-CU).
O-RU is a logical node contains RF and lower PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC and RLC. In addition, the O-CU depicts the logical node contains two parts, which are O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP and
O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real Time and O-Cloud. 
One of the necessities of new generation of wireless networks is its intelligence.
Based on the requirement of smart wireless network, O-RAN offers machine learning techniques.
The two logical nodes RIC-Non Real Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML}.

In the concept of network slicing, a slice is an end-to-end logical network
which offers services with special needs. 
Multiple isolated network slices run and manage
and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires special slice of network based on its QoS
 \cite{shen2020ai,setayesh2020joint}.

Some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.

>>>>

\begin{abstract}
Taking advantage of both virtual RAN (v-RAN) and Cloud RAN (C-RAN), Open RAN (O-RAN) is introduced as the next generation of RAN systems which leads to increase flexibility, Openness, and reduce operational costs and allow them to add new capabilities to the network more quickly.
O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU), and Central Unit (O-CU).
In this paper, we study the problem of baseband resource allocation and virtual network function (VNF) activation in O-RAN architecture based on their service priority for a different types of 5G services includes enhanced mobile broadband (eMBB), ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services.
According to the concept of network slicing, the isolation of different types of services in O-DU, O-CU, and user plane function (UPF) is performed.
Limited fronthaul capacity and the restriction of end-to-end delay are considered in the problem.
The optimization of baseband resources includes O-RU assignment, physical resource block (PRB), and power allocation. The main problem is mixed-integer non-linear programming that is tremendously difficult.
To solve the challenging problem, we broke it down into two different steps that the iterative algorithm solves.
In the first step, we reformulated and simplified the problem to find the power allocation, PRB assignment, and the number of activated VNFs. In the second step, the O-RU association is carried out.
The proposed method is confirmed by the simulation results in a way that
the simulations illustrate a higher achievable data rate than a baseline scheme that only optimizes one of the baseband resources.

@@

\begin{IEEEkeywords}
Open Radio Access Network (O-RAN), Virtual Network Function (VNF) 
\end{IEEEkeywords}

\section{Introduction} 
Nowadays, RAN virtualization attracts significant attention from  both industry and academia since it 
has remarkable benefits which leads to increase the flexibility and 
reduce operator costs
such as CAPEX and OPEX and also allow them to add new capabilities to the network more quickly.
In addition to RAN virtualization, openness and RAN intelligence are two other fundamental points that encourage Open Radio Access Network (O-RAN)
Alliance to establish O-RAN as a next generation of RAN systems. 
The idea of O-RAN comes from the integration of virtual RAN (vRAN) and cloud RAN (CRAN) and it takes the advantage of both.
CRAN, divides RAN into two parts radio remote head (RRH) and base band unit (BBU). 
More than one distributed RRHs can be connected to a centralized BBU which is named BBU-pool\cite{han2019research}.
Unlike previous generation of RAN that divide RAN into two parts, O-RAN separate RAN into three different units, namely Radio Unit (O-RU), Distributed Unit (O-DU) and
Central Unit (O-CU).
O-RU is a logical node contains RF and lower PHY. Moreover, the O-DU expresses another logical node that includes higher PHY, MAC and RLC. In addition, the O-CU depicts the logical node contains two parts, which are O-CU user plane (O-CU-UP) and O-CU control plane (O-CU-CP). O-CU-UP hosts PDCP-UP and SDAP and
O-CU-CP hosts PDCP-CP and RRC.
O-DU and O-CU are connected to each other via an open and well-defined interface $F_1$.
Moreover, O-DU is connected to radio unit (O-RU) with an open fronthaul interface.
The architecture of O-RAN contains other principal logical nodes called Orchestration and Automation,
RAN Intelligent Controller (RIC)- Near Real Time and O-Cloud. 
One of the necessities of new generation of wireless networks is its intelligence.
Based on the requirement of smart wireless network, O-RAN offers machine learning techniques.
The two logical nodes RIC-Non Real Time (which is placed in Orchestration and Automation node) and RIC- Near Real Time implement the algorithms for network intelligence 
\cite{gavrilovska2020cloud,niknam2020intelligent,kazemifard2021minimum,both2021system,ORANArch,ORANML}.

In the concept of network slicing, a slice is an end-to-end logical network
which offers services with special needs. 
Multiple isolated network slices run, manage
,and work independently on the same infrastructure. There are several implementations of network slicing, including network core slicing, RAN slicing, and slicing of both sections. 
Different type of services includes enhanced mobile broadband (eMBB) and ultra-reliable low latency communications (URLLC) and massive Machine Type Communications (mMTC) services are introduced in 5th generation of mobile network. Each type of service requires special slice of network based on its QoS
 \cite{shen2020ai,setayesh2020joint}.

To improve system performance in the fifth generation of telecommunications, the separation of network software and hardware elements has been done and introduced as network function virtualization (NFV), and virtual network functions (VNF) are system function blocks. The key idea of the implementation of NFV is 
to decouple software from physical hardware, dynamic scaling and the deployment of flexible network function. A usual NFV offer is to execute VNFs on a virtual machines or containers in a cloud system \cite{mijumbi2015network, luo2020online}.
As a result, some O-RAN components that includes user plane function (UPF) , O-CU, O-DU and RAN Intelligent Controller (RIC)-near real time, are virtualized and implemented as a VNF that can be run on virtual machines (VMs) or containers.
\subsection{Related Works}
In \cite{SystemCostMinimization}, the authors solve the problem of obtaining beamforming and VMs activation 
in C-RAN system with limited fronthaul capacity. The goal of the paper is to minimize the energy cost, with the system delay, fronthaul capacity and rate constraint.
